---
output:
  md_document:
    variant: gfm
html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# Using clusterProfiler to characterize Multi-Omics Data

If you use this work in published research, please cite:

Using clusterProfiler to characterize Multi-Omics Data

This repo contains source code and data to produce Figures of the above paper.
  
  The `IBD_2_subtypes_example`, `Phyllostachys_heterocyla_example` and `single_cell_example` contain the 
  data, scripts and results of the three examples in the above article. Each sub directory contains 
  `input_data`, `result`, `script`.

  + input_data: contains all the data sets that used to generate the figures.
  + result: contains the results.
  + script: contains the source code to produce the figures.

More details information can be found from [here](https://yulab-smu.top/clusterProfiler_protocol/).

## Dependencies and locations
  
```{r, message=FALSE, echo=FALSE, warning = FALSE, setup}
library(tictoc)
library(MicrobiotaProcess)
library(clusterProfiler)
library(ggplot2)
library(enrichplot)
library(dplyr)
library(aplot)
library(DESeq2)
library(ggfun)
library(Seurat)
library(CelliD)
library(ggrepel)
library(ggsc)
library(patchwork)
library(gridExtra)
```


Here is the output of `sessionInfo()` of the system was compiled:

```{r, echo=FALSE}
sessionInfo()
```

