---
title: "Using clusterProfiler to characterize Multi-Omics Data"
subtitle: "online example data"
author: "Maintained by YuLab-SMU"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
  pdf_document:
    toc: true
---



```{r echo=FALSE, results="hide", message=FALSE, warning=FALSE}
library(fs)
library(knitr)
```
# Data description

## Phyllostachys Edulis example data description:

Phe_GO_annotation.txt: The Phyllostachys Edulis gene GO annotation data was downloaded from https://plantregmap.gao-lab.org/download_ftp.php?filepath=08-download/Phyllostachys_heterocycla/GO/Phe_GO_annotation.gz.

Phe_TF_list.txt: The Phyllostachys Edulis transcription factor family annotation data was downloaded from https://planttfdb.gao-lab.org/download/TF_list/Phe_TF_list.txt.gz.

regulation_from_motif_CE_Phe.txt: The Predicted Phyllostachys Edulis transcription factor target gene was downloaded from https://plantregmap.gao-lab.org/download_ftp.php?filepath=08-download/Phyllostachys_heterocycla/binding/regulation_from_motif_CE_Phe.txt.

counts.txt: The counts.txt was processed Phyllostachys Edulis gene count matrix derived from https://db.cngb.org/search/project/CNP0002243/.

group_info.txt: The Phyllostachys Edulis sample group infomation was derived from https://onlinelibrary.wiley.com/doi/10.1111/jipb.13357.

# Data link
```{r echo=FALSE}
library(fs)
x <- dir_info('./', recurse = TRUE)[, 1:3] |>
    as.data.frame() |> subset(type == "file") |>
    subset(!path %in% c("index.Rmd", "index.html", "render.sh"))

x$path <- sprintf("[%s](%s)", x$path, x$path)

knitr::kable(x, row.names = FALSE)
```
