---
title: "Using clusterProfiler to characterize Multi-Omics Data"
subtitle: "online example data"
author: "Maintained by YuLab-SMU"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
  pdf_document:
    toc: true
---



```{r echo=FALSE, results="hide", message=FALSE, warning=FALSE}
library(fs)
library(knitr)
```
# Data description

## Inflammatory Bowel Disease example data description

NIHMS1510763-supplement-Dataset_1.xlsx: The Metabolomic Abundance Raw Matrix was downloaded from https://doi.org/10.1038/s41564-018-0306-4.

NIHMS1510763-supplement-Dataset_2.xlsx: The Metabolite Original ID and Metabolite Name Conversion Table was downloaded from https://doi.org/10.1038/s41564-018-0306-4.

NIHMS1510763-supplement-Dataset_6.xlsx: The Metagenomic Original Gene Abundance Matrix File was downloaded from https://doi.org/10.1038/s41564-018-0306-4.

enzyme_ko.txt: The ID mapping file (mapping enzymes to KEGG K-Numbers) was downloaded from https://github.com/YuLab-SMU/Supplemental-MMINP/blob/main/data/20220924_kegg/enzyme_ko.txt.

metabolwasm_expr.csv: The processed metabolomic abundance matrix file was derived from https://doi.org/10.1038/s41564-018-0306-4.

metabolwasm_meta.csv:  The processed metabolomic experimental grouping information file was derived from https://doi.org/10.1038/s41564-018-0306-4.

mg.expr.csv: The processed metagenomic abundance matrix file was derived from https://doi.org/10.1038/s41564-018-0306-4.

mg.meta.csv:  The processed metabolomic experimental grouping information file was derived from https://doi.org/10.1038/s41564-018-0306-4.

name_map.csv: The ID mapping file(mapping metabolites to KEGG C-Numbers) was downloaded from https://www.metaboanalyst.ca/MetaboAnalyst/resources/users/guest7299843510837833804tmp/name_map.csv.


# Data link
```{r echo=FALSE}
library(fs)
x <- dir_info('./', recurse = TRUE)[, 1:3] |>
    as.data.frame() |> subset(type == "file") |>
    subset(!path %in% c("index.Rmd", "index.html", "render.sh"))

x$path <- sprintf("[%s](%s)", x$path, x$path)

knitr::kable(x, row.names = FALSE)
```
